### 2016-11-29 local-capability-machine.tex
further changes related to the new standard regions
f2 proof

\begin{figure}
  \label{fig:stack-after-restore-code}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   & \\
   & $\vdots$\\
\cline{2-2}
   & ? \\
\cline{2-2}
$ \rightarrow$  & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
   & Restore code \\
   & $\vdots$\\
\cline{2-2}
 $c_\stk \rightarrow$  & local stack\\
   & $\vdots$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_\pc^{(3)}$\\
\cline{2-2}
$r_0$  &  $c_0$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}$ \\
\cline{2-2}
$r_1$ & $w_1$ \\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & $w_{p,m}$ \\
\cline{2-2}
& $?$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-register file after the clean up code has been run. The ``private'' words have been poped to their respective registers. The restore code has been poped off the stack. }
\end{figure}

@@

\item $\npair{c_\adv} \in \stder(W)$

@@

\item $\heapSat[\ms]{n}{W}$ \lau{The argument here is a bit informal}

@@

\item $\npair{\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''}} \in \stdrr(W)$

@@

      (From $\heapSat[\ms']{n''}{W'}$ we know that that $\ms'$ contains memory segments $\hs_{f2}$, $\hs_\flag$, and $\ms_\stk'|_{[\start_\stk, \start_\stk''-1]}$ (our local part of the stack). The restoration code remains unaltered, and so does the data on the stack, so the execution continues by poping the $c_\stk'$ to $r_\stk$ followed by a pop of $c_{f2}'$ to $\pcreg$. Continuing in $f2$, the restore code is poped off the stack which is the last of the $\mathtt{scall}$ instruction. Now the top word of the stack is poped to $r_1$, and thanks to the world satisfaction, we know that this word is 1. The $\mathtt{assert}$ therefore succeeds making no changes to the memory and afterwards the execution halts.)

Use $\revokeTemp(W') \futurestr W'$. From the private-future memory satisfaction lemma (Lemma~\ref{lem:priv-mono-like}) get $\ms''$ and $\ms_f$ such that

    \item case $r\not\in \{\pcreg,r_0,r_1,r_\stk\}$: $\reg_0(r) = 0$. Trivial.
  \end{enumproof}
\end{enumproof}
to get

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^\pwl : \Views \fun \Regions\\
  &\iota_{\start,\addrend}^\pwl \defeq (\temp,1,=,H^\pwl_{\start,\addrend}) & v \neq \revoked \\
\\
  &H^\pwl : \Addrs^2 \fun \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^\pwl_{\start,\addrend}\; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi_{\var{wk}}(\hat{W}))
    \end{aligned}
  \right\}
\end{align*}
\lau{What is the reason to have the ``view'' always be $\temp$? It seems like it does not play well with the read condition if it is always $\temp$.}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

>>>>

\begin{figure}
  \label{fig:stack-after-restore-code}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   & \\
   & $\vdots$\\
\cline{2-2}
   & ? \\
\cline{2-2}
$ \rightarrow$  & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
   & Restore code \\
   & $\vdots$\\
\cline{2-2}
 $c_\stk \rightarrow$  & local stack\\
   & $\vdots$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_\pc^{(3)}$\\
\cline{2-2}
$r_0$  &  $c_0$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}$ \\
\cline{2-2}
$r_1$ & $w_1$ \\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & $w_{p,m}$ \\
\cline{2-2}
& $?$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-register file after the clean up code has been run. The ``private'' words have been popped to their respective registers. The restore code has been popped off the stack. }
\end{figure}

@@

\item $\npair{c_\adv} \in \stder(W)$ \label{lem:f2-adv-er}

@@

\item $\heapSat[\ms]{n}{W}$ \label{lem:f2-mem-sat}\lau{The argument here is a bit informal}

@@

\item $\npair{\reg_0\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''}} \in \stdrr(W)$ \label{lem:f2-reg-rel}

@@

      From $\heapSat[\ms']{n''}{W'}$ we know that that $\ms'$ contains memory segments $\hs_{f2}$, $\hs_\flag$, and $\ms_\stk'|_{[\start_\stk, \start_\stk''-1]}$ (our local part of the stack). The restoration code remains unaltered, and so does the data on the stack, so the execution continues by popping the $c_\stk'$ to $r_\stk$ followed by a pop of $c_{f2}'$ to $\pcreg$. Continuing in $f2$, the restore code is popped off the stack which is the last of the $\mathtt{scall}$ instruction. Now the top word of the stack is popped to $r_1$, and thanks to the world satisfaction, we know that this word is 1. The $\mathtt{assert}$ therefore succeeds making no changes to the memory and afterwards the execution halts.

All in all, there are no changes to the memory, so we can conclude
\[
  m'' = \ms' \uplus \ms_f
\]
From Lemma~\ref{lem:priv-mono-like}, we can get $\ms''$ and $\ms_r$ such that
\begin{itemize}
\item $\ms' = \ms'' \uplus \ms_r$
\item $\heapSat[\ms'']{n}{\revokeTemp{W}}$
\end{itemize}
Now downwards closure of memory segment satisfaction gives us the desired result.
    \item case $r\not\in \{\pcreg,r_0,r_1,r_\stk\}$: $\reg_0(r) = 0$. Trivial.
  \end{enumproof}
\end{enumproof}
From \ref{lem:f2-adv-er}, \ref{lem:f2-mem-sat}, and \ref{lem:f2-reg-rel} it follows that
\[
  \npair{(\reg_0\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''}\update{\pcreg}{c_\adv},\ms)} \in \observations(W)
\]
Now using $i$, the number of steps we need to halt, $\ms_f$ as the frame, $m'$ as the resulting memory and the assumption that the execution terminates successfuly gives $W' \futurestr W$, $\ms'$, and $\ms_r$ such that
\begin{itemize}
\item $m' = \ms' \uplus\ms_r \uplus \ms_f$
\item $\heapSat[\ms']{n-i}{W'}$
\end{itemize}
The permanent region $\iota^\sta (\perma,\ms_\flag)$ ensures that $\ms_\flag$ is unchanged, so
\[
  m'(\flag) = 0
\]
\end{proof}

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^\pwl : \Regions\\
  &\iota_{\start,\addrend}^\pwl \defeq (\temp,1,=,H^\pwl_{\start,\addrend}) \\
\\
  &H^\pwl : \Addrs^2 \fun \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^\pwl_{\start,\addrend}\; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi_{\var{wk}}(\hat{W}))
    \end{aligned}
  \right\}
\end{align*}
\lau{What is the reason to have the ``view'' always be $\temp$? It seems like it does not play well with the read condition if it is always $\temp$.}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}
